Actuator line modeling of vertical-axis turbines

### 2016-08-27 paper.tex
Add default Smagorinsky coeff value

Thus, the UNH-RVAT baseline case was simulated using the Smagorinsky LES
turbulence model \cite{Smagorinsky1963}, which was the first of its kind, and
serves as a good standard for LES modeling since its behavior is well-reported
in the literature. Default Smagorinsky model coefficients were used, and the LES
filter width was set as the cube root of the local cell volume. The tip speed
ratio was set to oscillate sinusoidally about $\lambda_0$ with a 0.19 magnitude
and the angle of the first peak at 1.4 radians---similar to the rotation
presribed in the blade-resolved RANS simulations discussed in
\cite{Bachant2016-BR-CFD}.

>>>>

Thus, the UNH-RVAT baseline case was simulated using the Smagorinsky LES
turbulence model \cite{Smagorinsky1963}, which was the first of its kind, and
serves as a good standard for LES modeling since its behavior is well-reported
in the literature. OpenFOAM's default Smagorinsky model coefficients were used
(giving an approximate equivalent Smagorinsky coefficient $C_S = 0.17$), and the
LES filter width was set as the cube root of the local cell volume. The tip
speed ratio was set to oscillate sinusoidally about $\lambda_0$ with a 0.19
magnitude and the angle of the first peak at 1.4 radians---similar to the
rotation presribed in the blade-resolved RANS simulations discussed in
\cite{Bachant2016-BR-CFD}.
